%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Personal Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventryprojects
    {Network Tower Position Optimizer Using Machine Learning} % Brief Description
    {Tethr} % Title
    {Python, C++} % Language
    {2023} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Developed a robotic system that uses ML to optimize 5G network tower locations 
        to solve cellphone signal abruptions.}
        \item {Integrated a custom-built drone and an automated LIDAR-based ground robot to automate the process of 
        data collection.}
        \item {Incorporated non-parametric and density-based Mean Shift clustering algrorithm, and Gradient Descent 
        for optimization.}
        \item {Used YoloV8 for object detection and Jetson Nano for onboard computing to improve accuracy of the automated 
        ground robot.}
        \item {Desinged a ground station using Tkinter to defined the robot path, load the data, and visualize the results.}
        \item {\underline{Utilized:} Python, C++, Scikit-Learn, OpenCV, YoloV8, Pandas, Raspberry Pi, Jetson Nano, ROS, FastAPI, Tkinter.}
      \end{cvitems}
      }
      
      %---------------------------------------------------------
      \cventryprojects
      {Blockchain-Based Electricity Billing System } % Brief Description
      {Block Meter} % Title
      {Python, C++, Solidity} % Language
      {2022} % Date(s)
      {
        \begin{cvitems} % Description(s)
          \item {Invented an electricity billing system that eliminated non-technical losses by 100\% and ensures transparency and immutability.}
          \item {Won a Silver Medal in SDG 12 national teams from 44 countries at the International Blockchain Olympiad 2022 (Hong Kong).}
          \item {Secured Bronze Medal as the youngest developer to secure top national position in the Bangladesh Blockchain Olympiad 2022.}
          \item {\underline{Utilized:} Python, C++, Solidity, PHP, Javascript, Ethereum, IPFS, BigChainDB, AES Encryption, ESP32, ThinkSpeak.}
        \end{cvitems}
        }
          
          %---------------------------------------------------------
          \cventryprojects
          {For additional information and projects (\href{https://hamidurrk.com}{hamidurrk.com})} % Brief Description
          {Portfolio Website} % Title
          {Next.js} % Language
          {2016-2022} % Date(s)
          {
            \begin{cvitems} % Description(s)
              \item {Developed a responsive portfolio website to showcase my projects, skills, and experiences using modern web technologies.}
              \item {Used Greensock and Framer Motion to create scroll-triggered animations, smooth transitions, and interactive elements.}
              \item {Built a real-time physics simulation world within the frontend to simulate bouncing shapes, exploding boxes and slow motion.}
              \item {\underline{Utilized:} Next.js, React.js, Typescript, Tailwind CSS, Framer Motion, GSAP, physics.js, Lenis, SCSS, Vercel.}
            \end{cvitems}
            }
        
        %---------------------------------------------------------
        \cventryprojects
        {Automated Social Media Interactor and Data Scraper} % Brief Description
        {Social Media Bot} % Title
        {Python} % Language
        {2018} % Date(s)
        {
          \begin{cvitems} % Project Description(s)
            \item { Developed a bot that automatically interacts with Facebook and Instagram to increase user engagement and scrapes data.}
            \item { Currently writing a paper with researchers at University of Kassel and Technical University of Dortmund on Political Propaganda Cycle 
            using the data collected by the bot from the political parties on the social media platforms.}
            \item { Designed a user-friendly GUI for easy interaction with data scraper using CustomTKinter for improving the debugging capabilities.}
            \item {\underline{Utilized:} Python, Selenium, BeautifulSoup, OpenCV, Pillow, CustomTKinter, Matplotlib, Sqlite3, Pandas.}
          \end{cvitems}
          }
            
            %---------------------------------------------------------
            \cventryprojects
            {Line Follower Robot with custom operating system} % Brief Description
            {Spectre Bot \& Spectre OS} % Title
            {C++} % Language
            {2016-2022} % Date(s)
            {
              \begin{cvitems} % Description(s)
                \item {Spectre bot is a fully custom advanced line 
                follower robot capable of achieving a maximum of 5m/s speed on track.}
                \item {Spectre OS is a custom operating system designed to provide advanced control and 
                debugging capabilities for line follower robots.}
                \item {Secured champion position in the International Tech Carnival-DRMC 2020 with Spectre Bot.}
                \item {\underline{Utilized:} C++, Arduino, ESP-32, TCRT5000 Sensors, PID controllers, OLED graphics, gear/servo motors, PCB designing, 3D printing.}
              \end{cvitems}
              }
%---------------------------------------------------------
\end{cventries}
