\documentclass[12pt, titlepage, a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}

\linespread{1.5}

\title{Background Information}
\author{Md Hamidur Rahman Khan}
\date{\today}

\begin{document}

\maketitle

\section{Introduction}
This document provides background information for possible tutor-teacher
discussions. It covers my origins, reasons for choosing LUT and the
Computational Engineering program, understanding of my study structure, 
career plans, and experiences during the fall semester.

\section{Where I Am From and Why I Chose LUT}

I am from Dhaka in Bangladesh. It's a small tropical country in South Asia
with a large population. Our school system was quite competitive for this reason.
I grew a passion for programming and robotics during my high school years. 
Even though the hobby was challenging enough for a high school student, it was
quite rewarding too. During my school years, I participated in various 
robotics/programming competitions and won several national-level awards. 
By the time I finished high school, I was sure that I wanted to pursue a career
in robotics and programming. 

I started looking for universities that offered programs in these areas but 
specially I was looking for a program that was more versatile, practical, and 
focused on real-world applications. Unfortunately, there were not many options
in Bangladesh. So, I started looking for universities abroad with a similar focus.
Eventually, I found LUT and the Computational Engineering program which seemed
like a good fit. The program's focus on computational methods, artificial 
intelligence, and software engineering made it a good choice for me. Moreover,
I love the idea of studying in Finland, a country known for its high-quality
education system, revolutionary technologies, and beautiful nature.

\section{Study Structure and Specialization Plans}
I am glad to say that I have a clear understanding of the structure of my studies. 
The program is well-organized, and I am aware of the courses and requirements. 
I am considering specializing in LLM and Robotics for my master's studies. 
Additionally, due to my passion for programming, I am fixated on taking Software 
Engineering as my minor.

\section{Career Plans}
I am preparing myself for a career in the field of robotics and artificial intelligence.
I believe that these fields have a lot of potential for growth and innovation. Due to 
the recent advancements and the increasing demand for AI and automation, I think that 
I have a good chance to make a significant contribution to these fields. 

I am focusing on developing my skills in programming, machine learning, and LLM to 
become an ML engineer or a robotics engineer. I am also looking forward to 
internships and projects that will help me gain experience in these fields.  

\section{Fall Semester Experience}
I am happy to say that my studies at LUT are helping me a lot to develop skills and 
gain the knowledge required for the future roles that I have in mind. The courses 
that I have taken so far have been very helpful in understanding the foundations of 
the program. I am being able to enjoy programming as much as I did in high school. 

During the fall semester, I have tried to apply my knowledge from the mathematics
courses and apply them to better understand the Generative Transformer model. Currently,
I am working on rebuilding the GPT-2 model from scratch to understand its architecture.
I feel really good about the opportunities that LUT is providing me and I am looking
forward to the upcoming semesters to learn more and grow further.

\section{Conclusion}
As I am writing this document, I am realizing how much I love studying here at LUT. I 
hope to continue my studies with the same enthusiasm and passion. I am looking forward
to the future and the opportunities that LUT has to offer. I am excited to see what 
the future holds.

\end{document}